\section{Recovery using Escape theorem}\label{escapesec}
In the previous section, we observed that
a solution with small expected $\ell_2$ error can be obtained
using basis pursuit. In this section, we will
find the conditions under which the error becomes
zero.

\begin{theorem}\label{exactrecoverytheorem}
	In problem \eqref{problem0}, suppose $A\in\mathcal{A}(m, n)$ and
	$T = S$. If $m\geq CK^4 s\log n$, then with
	probability at least $1-2\exp(-cm/K^4)$,
	basis pursuit solves the sparse recovery problem
	(that is, $\hat{x} = x$).
	\end{theorem}
\begin{remark}
	The number of measurements $m$ depends linearly on
	sparsity $s$ and logarithmically on the dimension of
	the underlying space. This suggests that even for larger
	dimensional spaces, sparse recovery is possible with
	few meausrements.
\end{remark}
The main result that will be used to prove the theorem
is escape theorem, which states that the kernel of a matrix
with sub-gaussian rows misses sufficiently small subset of the unit sphere
with high probability.

\begin{theorem}\label{escapetheorem}
	Consider $T\subseteq S^{n-1}$. Let $A\in \mathcal{A}(m, n)$. If
	$m\geq CK^4w(T)^2$, then 
	$T\cap \ker(A) = \emptyset$ with probability at least
	$1-2\exp(-cm/K^4)$.
\end{theorem}
\begin{proof}
	The proof uses tail bound version of matrix deviation inequality,
	which states
	$$\sup_{a\in T}\abs{\pnorm{Aa}{2}-\sqrt{m}\pnorm{a}{2}}
		\leq CK^2(w(T)+u)$$
	with probability at least $1-2\exp(-u^2)$.
	Suppose the above event happens and $T\cap\ker(A)\neq\emptyset$.
	If $a\in T\cap\ker(A)$, then putting $u = \sqrt{m}/(2CK^2)$,
	the above
	inequality becomes $\sqrt{m}\leq CK^2w(T) + \sqrt{m}/2$. That is,
	$m \leq C'K^4w(T)^2$, which is contrary to the hypothesis. So
	$T\cap E = \emptyset$ happens with probability at least $1-2\exp(-(cm)/K^4)$
\end{proof}

Before proving theorem \ref{exactrecoverytheorem}, we
will prove the following lemma:

\begin{lemma}\label{lemma1er}
	Let $h = \hat{x} - x$
	\begin{enumerate}
			\item If $S = \supp(x)$, then $\pnorm{h_S}{1}\geq \pnorm{h_{S^c}}{1}$

			\item $\pnorm{h}{1}\leq 2\sqrt{s}\pnorm{h}{2}$
	\end{enumerate}
\end{lemma}

\begin{proof}
		Since $\hat{x}$ is the $\ell_1$ norm minimizer
			and $x_{S^c} = 0$,
			we have
			$0\geq \pnorm{\hat{x}}{1} - \pnorm{x}{1} = \pnorm{\hat{x}_S}{1}
			+ \pnorm{\hat{x}_{S^c}}{1} - \pnorm{x_S}{1} =
			(\pnorm{\hat{x}_S}{1} - \pnorm{x_S}{1}) + \pnorm{h_{S^c}}{1}
			\geq -\pnorm{\hat{x}_S- x_S}{1} + \pnorm{h_{S^c}}
			= -\pnorm{h_{S}}{1} + \pnorm{h_{S^c}}{1}$. This proves
			the first part.\\
	For the second part, 
	$\pnorm{h}{1} = \pnorm{h_S}{1} + \pnorm{h_{S^c}}{1}\leq 2\pnorm{h_S}{1}\leq 2\sqrt{s}\pnorm{h}{2}$
	%	\begin{enumerate}
%		\item $\pnorm{\hat{x}} =\pnorm{h+x}{1} = \pnorm{h_S + x_S}{1}
%			+ \pnorm{h_{S^C} + x_{S^C}}{1} = \pnorm{h_S + x_S}{1} +\pnorm{h_{S^C}}{1}
%			\geq \pnorm{x_{S}}{1} - \pnorm{h_S}{1} + \pnorm{h_{S^C}}{1}$
%			Now, $\pnorm{\hat{x}}{1} - \pnorm{x_S}{1}\leq 0$. This proves the result.

%		\item $\pnorm{h}{1} = \pnorm{h_S}{1}\leq 2\pnorm{h_S}{1}\leq 2\sqrt{s}\pnorm{h}{2}$
%	\end{enumerate}
\end{proof}
%\hfil
%\flushleft
%\begin{center}
\noindent
	\textit{Proof of theorem \ref{exactrecoverytheorem}.}
	Suppose $h\neq 0$, then $h/\pnorm{h}{2}\in S^{n-1}$. Also, from part 2 of
	the lemma, $h/\pnorm{h}{2}\in 2\sqrt{s}B_1^n$. So, if $T = S^{n-1}\cap (2\sqrt{s}B_1^n)$,
	then $h/\pnorm{h}{2}\in T\cap (\ker A)$, since $Ax = A\hat{x}$.
	Now, $m\geq CK^4 s\log n \geq C'K^4 w(T)^2$ (because $w(T)\leq w(2\sqrt{s}B_1^n$)),
	therefore, by theorem \ref{escapetheorem} $T\cap (\ker A) = \emptyset$ with high probability.
	Thus $\hat{x} = x$ with probability at least $1-2\exp(-cm/K^4)$.
%\end{center}
\indent
	\qed

\section{Recovery using RIP}\label{RIP}
Now we will consider a different class of matrices.
\begin{definition}
	An $m\times n$ matrix $A$ satisfies Restricted Isometry Property (RIP) with
	parameters $\alpha, \beta$ and $s$ if for every $s$-sparse vector
	$w$,
	\begin{equation*}
		\alpha \pnorm{w}{2}\leq \pnorm{Aw}{2}\leq \beta\pnorm{w}{2}.
	\end{equation*}
	The set of $m\times n$ matrices satisfying RIP with parameters
	$\alpha, \beta$ and $s$ will be denoted by
	$RIP(m,n,\alpha, \beta, s)$.
\end{definition}

\begin{remark}\label{ripremark}
	It is clear from the definition that $A$ satisfies RIP with
	parameters $\alpha, \beta$ and $s$ if
	and only if all the singular values of all $m\times s$ sub-matrices
	of $A$ lie between $\alpha$ and $\beta$.
\end{remark}

\begin{theorem}[Candes--Tao]\label{ripimpliesexact}
	Suppose in \eqref{problem0}, $A$ satisfies RIP with parameters
	$\alpha, \beta$ and $(1+\lambda)s$, with $\lambda >
	(\beta/\alpha)^2$. Then basis pursuit \eqref{basispursuit}
	exactly recovers the slolution to the sparse recovery problem.
\end{theorem}

\begin{proof}
	Let $h_I\in \R^{|I|}$ denote
	the projection of $h$ onto the subset of indices $I$.
	Let $I_0$ be the support of $x$,
	$I_1$ be the $\lambda s$ largest indices of $h_{I_0^c}$,
	$I_2$ be the next $\lambda s$ largest indices and so on.
	Let $I_{0,1} = I_0 \cup I_1$. For any set of indices
	$I\subseteq \{1,\ldots n\}$, let $A_I$ be the $m\times |I|$
	submatrix of $A$ with all but the columns in $I$ deleted.
	Let $h = \hat{x}-x$.\\
	By triangle inequality,
$	
		\pnorm{Ah}{2} = \pnorm{A_{I_{0,1}}h_{I_{0,1}} + A_{I_{0,1}^c}h_{I_{0,1}^c}}{2}\geq \pnorm{A_{I_{0,1}}h_{I_{0,1}}}{2} - \pnorm{A_{I_{0,1}^c}h_{I_{0,1}^c}}{2}
$.
Left hand side is zero, since $Ah = A\hat{x} - Ax = 0$.
So,
	\begin{equation}\label{cond1}
		\pnorm{A_{I_{0,1}}h_{I_{0,1}}}{2}\leq \pnorm{A_{I_{0,1}^c}h_{I_{0,1}^c}}{2}.
	\end{equation}
Now, by RIP,
	 \begin{equation}\label{cond2}
		 \alpha \pnorm{h_{I_{0,1}}}{2}\leq \pnorm{A_{I_{0,1}}h_{I_{0,1}}}{2}.
	 \end{equation}
By triangle inequality and RIP,
		\begin{equation}\label{aboveinequality}
            \pnorm{A_{I_{0,1}^c}h_{I_{0,1}^c}}{2} 
			\leq  \sum_{j\geq 2} \pnorm{A_{I_j}h_{I_j}}{2}
            \leq \beta\sum_{j\geq 2}\pnorm{h_{I_j}}{2}.
        \end{equation}
Now observe that for any $j$,
        $
		\pnorm{h_{I_j}}{2}\leq \sqrt{\lambda s}\frac{\pnorm{h_{I_{j-1}}}{1}}{{\lambda s}}
        $.
	Substituting this in \eqref{aboveinequality} gives
        \begin{equation}\label{eqpen}
			\pnorm{A_{I_{0,1}^c}h_{I_{0,1}^c}}{2}\leq (\beta/\sqrt{s\lambda)}\pnorm{h_{I_0^c}}{1}.
        \end{equation}
    From the first part of lemma \ref{lemma1er}, $\pnorm{h_{I_0^c}}{1}\leq \pnorm{h_{I_0}}{1}$
    By Cauchy-Schwarz inequality, $\pnorm{h_{I_0}}{1}\leq \sqrt{s}\pnorm{h_{I_0}}{2}$
    Substituting this in \eqref{eqpen}, we get
    $
        \pnorm{A_{I_{0,1}^c}h_{I_{0,1}^c}}{2}\leq \frac{\beta}{\sqrt{\lambda}}\pnorm{h_{I_0}}{2}.
    $
    From \eqref{cond1}, \eqref{cond2} and the previous inequality, we get
    $
        \alpha \pnorm{h_{I_{0,1}}}{2} \leq \frac{\beta}{\sqrt{\lambda}} \pnorm{h_{I_{0}}}{2}
    $.
    From the condition on $\alpha,\beta, \lambda$, This can happen only if $\pnorm{h_{I_{0,1}}}{2} = 0$.
    Since $0 = \pnorm{h_{I_1}}{2}\geq \pnorm{h_{I_2}}{2}\geq \ldots$, we must have $h_{I_0^c} = h_{I_0} = 0$.
\end{proof}

Even though RIP gives a sufficient condition for exact
recovery, constructing matrices that satisfy RIP is difficult.
However, one can generate random matrices that satisfy RIP
with high probability. Surprisingly, a sample from the collection
$\mathcal{A}(m, n)$, that we saw in the previous section
satisfies RIP with good parameters, with high probability.
In order to prove such a result, we need bounds on the singular values.
We will use
the following bound on the singular values in the proof.
\begin{theorem}\label{singularvaluebounds}
	If $A\in\mathcal{A}(m, n)$, then for any
	$t\geq 0$,
	\begin{equation}\label{singularvalueboundeq}
		\sqrt{m} - CK^2(\sqrt{n}+t)\leq s_m(A_I)\leq s_1(A_I)
			\leq \sqrt{m} + CK^2(\sqrt{n}+t)
	\end{equation}
	with probability at least $1-2\exp(-t^2)$. (here $s_i(A)$
	represents the $i$th singular value of $A$ and $K$ is as before)
\end{theorem}
\noindent
% \textit{Sketch of proof: }
The proof of uses the result that the operator norm
$\norm{\frac{1}{m}A^TA - I_n}\leq \max(\delta, \delta^2)$ implies
all the singular values of $A/\sqrt{m}$
lie between $1-\delta$ and $1+\delta$.\\
An $\epsilon$ net $\mathcal{N}$ is used to bound
the supremum over the unit circle by a supremum over a
finite set.
%$$\sup_{x\in S^{n-1}}\ip{(\frac{1}{m}A^TA-I_n)x}{x}\leq 
%C(\epsilon)\sup_{x\in\mathcal{N}}\ip{(\frac{1}{m}A^TA-I_n)x}{x}.$$
After that, Bernstein's inequality is used to find tail bounds
for ${\ip{(\frac{1}{m}A^TA-I_n)x}{x}} = 
\abs{\pnorm{\frac{Ax}{\sqrt{m}}}{2}^2 - 1} = 
\sum_i \frac{1}{m}(\ip{A_i}{x}^2-1)$.
Then a union bound over $\mathcal{N}$ is taken
and finally, an appropriate value of $\delta$ is chosen
to arrive at \eqref{singularvalueboundeq}.
\indent

We can now use the bound \eqref{singularvalueboundeq} to
generate random matrices that satisfies RIP with high probability.

\begin{theorem}[Candes--Tao, 2005]\label{randomripprop}
	Suppose $A\in\mathcal{A}(m, n)$. If $m\geq CK^4 s\log n$, then
	$A\in RIP(m, n, 0.9, 1.1, s)$ with probability
	at least $1-2\exp({-cm}/{K^4})$.
\end{theorem}
\noindent
\textit{Sketch of proof:}
	From remark \ref{ripremark}, we need to bound the singular values
	for each $m\times s$ submatrix of $A$.
	Using theorem \ref{singularvaluebounds}, bound for singular
	values of each possible $m\times s$ submatrix $A_I$ can
	be bounded. Since there are only $\binom{n}{s}$ such matrices,
	we can use a union bound and use $\binom{n}{s}\leq n^s$.
	%Fix a subset $I$, of size $s$, of $\{1,\ldots, n\}$.
	%Consider the $m\times s$ submatrix $A_I$.
	%Applying the bounds on singular values of random matrices with
	%mean zero, isotropic, subgaussian rows to $A_I$, we get:
	%\begin{equation*}
	%	\sqrt{m} - CK^2(\sqrt{s}+t)\leq s_s(A_I)\leq s_1(A_I)
	%		\leq \sqrt{m} + CK^2(\sqrt{s}+t)
	%\end{equation*}
	%for any $t\geq 0$, with probability at least $1-2\exp(-t^2)$.
	%Putting $t = \sqrt{m}/(DCK^2)$ and setting appropriate values
	%for the constants, we can get the singular values to be
	%bounded by $0.9\sqrt{m}$ and $1.1\sqrt{m}$ with probability
	%at least $1-2\exp(-2mc_1/K^4)$ (Here $2c_1 = 1/(D^2C^2)$).
	%A union bound can be used to find the probability that
	%this happens for each subset $I$ of size $s$. This gives
	%the probability that $A$ satisfies RIP to be at least
	%$1-2\exp(\frac{-2mc_1}{K^4})\binom{n}{s}$. Now, using
	%$\binom{n}{s}\leq n^s$, the bound on the probability becomes
	%$1-2\exp(\frac{-2mc_1}{K^4}+s\log n)$. From the hypothesis,
	%the exponent is at most $-\frac{mc_1}{K^4}$, proving the result.
%\end{proof}
	\qed
\indent

\begin{remark}
	The above theorem can be used to prove theorem
	\ref{exactrecoverytheorem}: By replacing $s$ by $3s$
	in the theorem, $A$ satisfies RIP with parameters
	$0.9\sqrt{m}, 1.1\sqrt{m}$ and $3s$ with probability
	at lest $1-2\exp(-cm/K^4)$. 
	$A$ then satisfies the hypothesis of theorem
	\ref{ripimpliesexact} with $\lambda = 2\geq (1.1/0.9)^2$.
	Thus exact recovery of $s$-sparse signals is possible by
	the conclusion of theorem \ref{ripimpliesexact}.
\end{remark}

\subsection{Recovering signal from partial Fourier coefficients}
	In this section we will consider the case when the
	measurement matrix $A$ in \eqref{problem0} is
	a fourier sub-matrix. In this section,
	a signal $f$ is a vector in $\R^n$. The coordinates $f_n$
	will be denoted by $f(n)$. We will also be dealing with
	signals in $\C^n$, which poses no difficulty since all
	the analysis
	done so far in this section for signals in $\R^n$ can be
	extended to complex signals.
	\begin{definition}
		The \emph{discrete fourier transform} of a signal $f\in \R^n$
		is given by $\hat{f} = \mathcal{F}f$,
		where $\mathcal{F}\in \R^{n\times n}$ is the fourier matrix,
		whose $(a, b)$th entry is $\mathcal{F}(a,b) =
		e^{(i2\pi ab)/n}/\sqrt{n}$.
	\end{definition}
	The	matrix $\mathcal{F}$ is a unitary matrix.
	The domain of $f$ is called \emph{time} and the
	domain of $\hat{f}$ is
	called \emph{frequency}.
	Since
	$f = \mathcal{F}^* \hat{f}$, we can write $f(n)$ as
	a linear combination of $\hat{f}(t)$ for $t = 1,\ldots, n$.
	So, $\hat{f}(t)$s are also called the \emph{fourier coefficients}
	of $f$.

	Suppose a subset of fourier coefficients is known.
	The objective is to recover the signal $f$, given that
	$f$ is sparse. In order to obtain a sufficient
	condition for recovery to be possible we make the
	following definition.

	\begin{definition}
		Let $\Omega$ be a subset of frequency domain.
		Let $\hat{f}_{\Omega} = \mathcal{F}_\Omega f$, where
		$\mathcal{F}_\Omega$ is the $\abs{\Omega}\times n$
		sub matrix of $\mathcal{F}$ formed by the indices in
		$\Omega$. Then, $\Omega$ is said to have
		Restricted Isometry Propery with sparsity $s$ and
		error tolerance $\delta$, if for every $s$ sparse signal $f$,
		\[
			(1-\delta){\pnorm{f}{2}^2}/{N}\leq
			{\pnorm{\hat{f}_{\Omega}}{2}^2}/{\abs{\Omega}}\leq
			(1+\delta) {\pnorm{f}{2}^2}/{N}.
		\]
	\end{definition}
	On comparing this definition to the RIP
	property of matrices, it is clear that $\Omega$ satisfies
	RIP if and only if $\sqrt{N/\abs{\Omega}}\mathcal{F}_\Omega
	\in RIP(\abs{\Omega}, n,
	\sqrt{1-\delta}, \sqrt{1+\delta})$.
	Thus, by theorem \ref{ripimpliesexact}, the $s$-sparse
	signal $f$ can be recovered using basis pursuit
	if $\Omega$ has RIP with sparsity $4s$ and error tolerance
	$0.25$.


	This result by itself is not very different from
	the ones we have seen so far, since we do not know which
	subsets of frequency domain satisfies RIP. But the following
	theorem says any randomly chosen subset which is sufficiently
	large satisfies RIP.
	
	\begin{theorem}[Candes--Tao, 2006]
		A randomly chosen subset $\Omega$ of frequency domain
		of size $Cs\log^6 n$ will obey RIP with probability
		$1-O(N^{-C})$.
	\end{theorem}

	\noindent
	\textbf{Connection with Donoho-Stark uncertainty principle:} The
	reason why RIP guarantee
	exact recovery can be explained qualitatively by 
	Donoho-Stark uncertainty principle. It states that for a signal
	$f\in \R^n$, the product of the size of  supports, $\pnorm{f}{0}
	\cdot\pnorm{\hat{f}}{0}\geq n$. So, the sparser the signal,
	the larger is the support of its fourier transform.
	The condition for RIP roughly states that the
	$\ell_2$ norm of $f$ averaged over all the coordinates is
	aproximately equal to the $\ell_2$ norm of $\hat{f}$ averaged
	over the coordinates indexed by $\Omega$. Since $\mathcal{F}$
	is unitary, $\hat{f}$ and $f$ have the same $\ell_2$ norms.
	So, the total weight of $f$ is distributed
	to the coordinates of $\hat{f}$.
	If the support of $\hat{f}$ is large (i.e., when $f$ is sparse),
	even for smaller
	size of $\Omega$, the chances of missing the coordinates with
	the most weights are low. Hence RIP is satisfied even with
	smaller number of measurements.
	\indent
